### 2021-02-14 preliminaries.tex
Qualify CNF as first-order

A \emph{\acrfull{fol} problem} consists of a set of premise formulas and a conjecture formula.
In a \emph{refutation-based} \emph{\acrfull{atp}},
proving that the premises entail the conjecture
is reduced to proving that the premises together with the negated conjecture entail a \emph{contradiction}.
The most popular \gls{fol} \glspl{atp}, such as Vampire \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{},
start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in \emph{quantifier-free \gls{cnf}}.\cite{Harrison2009}
We denote a problem in \gls{cnf} as $P = (\Sigma, \mathrm{Cl})$,
where $\Sigma$ is a list of all non-logical symbols in the problem,
and $\mathrm{Cl}$ is the set of the clauses of the problem (including the negated conjecture).

>>>>

A \emph{\acrfull{fol} problem} consists of a set of premise formulas and a conjecture formula.
In a \emph{refutation-based} \emph{\acrfull{atp}},
proving that the premises entail the conjecture
is reduced to proving that the premises together with the negated conjecture entail a \emph{contradiction}.
The most popular \gls{fol} \glspl{atp}, such as Vampire \cite{10.1007/978-3-642-39799-8_1}, E \cite{10.1007/978-3-030-29436-6_29}, or SPASS \cite{},
start the proof search by converting the input \gls{fol} formulas to an equisatisfiable representation in \emph{quantifier-free first-order \gls{cnf}}.\cite{Harrison2009}
We denote a problem in \gls{cnf} as $P = (\Sigma, \mathrm{Cl})$,
where $\Sigma$ is a list of all non-logical symbols in the problem,
and $\mathrm{Cl}$ is the set of the clauses of the problem (including the negated conjecture).
